Paper_analyses

### 2021-09-09 Figures.Rmd
links

>>>>

supplemental

unique(db_full4new_stim_screen_pupil_nopract$ssid)

fix_dur_byval<-
db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(Group == "NT")%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
  group_by(ssid, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_ground_valence, mean_fix_dur))+
  # geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary(geom = 'pointrange',  size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_line(aes(group = ssid), alpha = .1)+
  p$graphstyle+
  theme(axis.text.x = element_text(size = 14, angle = 45), axis.title.x = element_blank())+
  xlab("Valence")+
  ylab("Average fixation duration (ms)")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  ggpubr::stat_compare_means(method = "t.test", paired =  TRUE)
  # facet_grid(~mediansplit_ground_valence)+
  # ylim(-3.3,1.3)

? ggpubr::stat_compare_means
fix_dur_byval

fix_dur_byval<-
db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(Group == "NT")%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
  group_by(ssid, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_ground_valence, mean_fix_dur))+
  # geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary(geom = 'pointrange', alpha = .1, size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_line(aes(group = ssid), alpha = .1)+
  p$graphstyle+
  theme(axis.text.x = element_text(size = 14, angle = 45), axis.title.x = element_blank())+
  xlab("Valence")+
  ylab("Average fixation duration (ms)")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  ggpubr::stat_compare_means(method = "t.test", paired =  TRUE)
  # facet_grid(~mediansplit_ground_valence)+

fix_dur_count<- db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(Group == "NT")%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
  group_by(ssid, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_ground_valence, fix_count))+
  # geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary(geom = 'pointrange', size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_line(aes(group = ssid), alpha = .1)+
  p$graphstyle+
    theme(axis.text.x = element_text(size = 14, angle = 45), axis.title.x = element_blank())+
  xlab("Valence")+
  ylab("Average fixation count")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  ggpubr::stat_compare_means(method = "t.test", paired =  TRUE)

# data loss
loss_dur_byval<- db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(Group == "NT")%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
  group_by(ssid, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_ground_valence, 1-gaze_valid_prop))+
  # geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary(geom = 'pointrange', size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_line(aes(group = ssid), alpha = .1)+
  p$graphstyle+
  theme(axis.text.x = element_text(size = 14, angle = 45), axis.title.x = element_blank())+
  xlab("Valence")+
  ylab("Average gaze loss (prop)")+
  # ylab("Baseline corrected pupil")+

  scale_color_brewer(palette = "Dark2")+
   scale_fill_brewer(palette = "Dark2")+
  ggpubr::stat_compare_means(method = "t.test", paired =  TRUE)

library(patchwork)
gaze_control <- fix_dur_byval+fix_dur_count+
loss_dur_byval

https://lvdmaaten.github.io/tsne/

ggsave("gaze_control.tiff",gaze_control, device = "tiff", width = 13, height = 6, dpi = 800)
https://www.r-bloggers.com/2017/09/multi-dimensional-reduction-and-visualisation-with-t-sne/
  https://cran.r-project.org/web/packages/Rtsne/Rtsne.pdf
https://uc-r.github.io/kmeans_clustering
```

3dplots
```{r}
clustering_agg_JASP
clustering_agg_JASPtest

clustering_agg_noflood$log_Bio_CDA.PhasicMax_z<- scale(clustering_agg_noflood$log_BIO_CDA.PhasicMax)

clustering_agg_noflood$Bio_Mean_HR_dif_z<- scale(clustering_agg_noflood$Bio_Mean_HR_dif)

clustering_agg_noflood$pup_basCor_z<- scale(clustering_agg_noflood$pup_basCor)

clustering_agg_noflood<- subset(clustering_agg, stimDescription != "Flood")
car::scatter3d(clustering_agg_noflood$log_Bio_CDA.PhasicMax_z, 
          clustering_agg_noflood$Bio_Mean_HR_dif_z, 
          clustering_agg_noflood$pup_basCor_z,
          fit = "smooth",
          point = FALSE,
          ellipsoid = TRUE,
          surface = FALSE,
          groups = clustering_agg_noflood$y_kmeans,
          point.col = clustering_agg_noflood$y_kmeans
          )

car::scatter3d(clustering_agg_noflood$log_Bio_CDA.PhasicMax_z, 
          clustering_agg_noflood$Bio_Mean_HR_dif_z, 
          clustering_agg_noflood$pup_basCor_z,
          fit = "smooth",
          point = FALSE,
          # ellipsoid = TRUE,
          surface = FALSE,
          groups = clustering_agg_noflood$y_kmeans,
          point.col = clustering_agg_noflood$y_kmeans
          )

# clustering_agg_JASP$clusters<- as.factor(clustering_agg_JASP$clusters)

clustering_agg_JASPtest$HR<-clustering_agg_JASPtest$Bio_Mean_HR_dif
clustering_agg_JASPtest$SCR<-clustering_agg_JASPtest$log_Bio_CDA.PhasicMax_z
clustering_agg_JASPtest$Pupil<-clustering_agg_JASPtest$pup_basCor_z

SCR<- clustering_agg_JASPtest$SCR
HR<- clustering_agg_JASPtest$HR
Pupil<- clustering_agg_JASPtest$Pupil
Cluster<- clustering_agg_JASPtest$clusters

car::scatter3d(SCR, 
          HR, 
          Pupil,
          # fit = "smooth",
          point = TRUE,
          ellipsoid = TRUE,
          surface = FALSE,
          groups = Cluster,
          point.col = Cluster
          )

car::scatter3d(clustering_agg_JASPtest$log_Bio_CDA.PhasicMax_z, 
          clustering_agg_JASPtest$Bio_Mean_HR_dif, 
          clustering_agg_JASPtest$pup_basCor,
          fit = "smooth",
          point = TRUE,
          # ellipsoid = TRUE,
          # surface = FALSE,
          groups = Cluster,
          point.col = Cluster
          )

car::scatter3d(SCR, 
          HR, 
          Pupil,
          fit = "smooth",
          point = TRUE,
          ellipsoid = TRUE,
          surface = FALSE,
          groups = Cluster,
          point.col = Cluster
          )
?car::scatter3d
car::scatter3d(SCR, 
          HR, 
          Pupil,
          fit = "smooth",
          point = TRUE,
          # ellipsoid = TRUE,
          surface = FALSE,
          groups = Cluster,
          point.col = Cluster
          )
```

### 2021-09-09 Paper_Analyses_subj_obje_arousal.Rmd
links

db_full4new_stim_screen_pupil_nopract%>%
  subset(Group == "NT")%>%
  group_by(ssid)%>%
  mutate(cor = cor(arousal, pup_basCor, use = "complete"))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ungroup()%>%
  ggplot(aes(TAS, cor))+
  geom_point(aes(color = ssid))+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

@@

summary(pupil_arousal_findings$BIO_CDA.PhasicMax)
anova(pupil_arousal_findings$arousal_phas_max)
interactions::interact_plot(pupil_arousal_findings$BIO_CDA.PhasicMax, pred = arousal_c, modx = valence_c)

@@

@@

clustering_agg$AlexGroup<- if_else(clustering_agg$TAS> median(clustering_agg$TAS, na.rm = TRUE), "High", "Low")
colnames(clustering_agg)
clust_dataset = clustering_agg[c(25,24,20)]

@@

# Fitting K-Means to the dataset
set.seed(1)
kmeans = kmeans(x = clust_dataset, centers = 3)
y_kmeans = kmeans$cluster

@@

a few visualisations
```{r}
clustering_agg$y_kmeans<- y_kmeans

?car::scatter3d
View(clustering_agg)
clustering_agg$y_kmeans<- as.factor(as.character(clustering_agg$y_kmeans))

@@

car::scatter3d(clustering_agg$log_Bio_CDA.PhasicMax_z, 
          clustering_agg$Bio_Mean_HR_dif_z, 
          clustering_agg$pup_basCor_z,
          fit = "smooth",
          point = FALSE,
          # ellipsoid = TRUE,
          # surface = FALSE,
          groups = clustering_agg$y_kmeans,
          point.col = clustering_agg$y_kmeans
          )

>>>>

db_full4new_stim_screen_pupil_nopract %>%
  subset(Group == "NT")%>%
  group_by(ssid)%>%
  mutate(cor = cor(arousal, pup_basCor, use = "complete"))%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ungroup()%>%
  ggplot(aes(TAS, cor))+
  geom_point(aes(color = ssid))+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()

@@

summary(pupil_arousal_findings$BIO_CDA.PhasicMax)

sjplot::tab_model(pupil_arousal_findings$BIO_CDA.PhasicMax)
anova(pupil_arousal_findings$arousal_phas_max)
interactions::interact_plot(pupil_arousal_findings$BIO_CDA.PhasicMax, pred = arousal_c, modx = valence_c)

@@

unique(db_full6new_hr_fix_stim_nt1.1$ssid)
db_full6new_hr_fix_stim_nt1.1
car::scatter3d(x = db_full6new_hr_fix_stim_nt1.1$pup_basCor, 
          y = db_full6new_hr_fix_stim_nt1.1$BIO_CDA.PhasicMax_z, 
          z = db_full6new_hr_fix_stim_nt1.1$Bio_Mean_HR_dif, 
          fit = "smooth",

@@

clustering_agg$AlexGroup<- if_else(clustering_agg$TAS> median(clustering_agg$TAS, na.rm = TRUE), "High", "Low")
colnames(clustering_agg)
clust_dataset = clustering_agg_noflood[c(25,24,20)]

@@

# Fitting K-Means to the dataset
set.seed(25)
kmeans = kmeans(x = clust_dataset, centers = 3)
y_kmeans = kmeans$cluster

@@

a few visualisations
```{r}
clustering_agg_noflood$y_kmeans<- y_kmeans

?car::scatter3d
View(clustering_agg)
clustering_agg_noflood$y_kmeans<- as.factor(as.character(clustering_agg_noflood$y_kmeans))

@@

car::scatter3d(clustering_agg$log_Bio_CDA.PhasicMax_z, 
          clustering_agg$Bio_Mean_HR_dif_z, 
          clustering_agg$pup_basCor_z,
          fit = "smooth",
          point = TRUE,
          # ellipsoid = TRUE,
          surface = FALSE,
          groups = clustering_agg$y_kmeans,
          point.col = clustering_agg$y_kmeans
          )
